Case Study: ChIP-seq Differential Peak Calling (csaw)

### 2018-07-06 datasets/ChIP-seq/ChIPseq-CBP-csaw.Rmd
Fix typo in filename

```{r}
plotMethodRanks(c(benchfile, benchfile_uninf), 
                colLabels = c("Region width", "Random"), 
                alpha = 0.10, xlab = "Covariate", 
                excludeMethods = NULL)
```

>>>>

```{r}
plotMethodRanks(c(bench_file, bench_file_uninf), 
                colLabels = c("Region width", "Random"), 
                alpha = 0.10, xlab = "Covariate", 
                excludeMethods = NULL)
```
